Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-03-09 thesis-main.tex
Drop unused \co command
Split thesis in parts
Split new.lhs and reorder chapters
Shuffle chapters more
Comment out the rewrite of change theory :-(.
Move PLDI14 contributions to intro
Add table of contents as requested
Move appendix on evaluation into evaluation
Change equivalence: finally drop sec-addendum
Misc. updates
Extra acknowledgments
Rearrange part I chapters
Discuss meta-language in intro to Part II
Move content from sec-formal into sec-intro.
Revise ToC for second part
Move sections to chapters and so on.
Fit huge figure into text
Just rotate and squeeze it a bit. Sorry.
Tentative t

\documentclass{book}
\usepackage{mylhs2tex}
\usepackage{natbib}
\usepackage{comment}
\bibliographystyle{abbrvnat}
\input{packages}
\input{macros}

\usepackage{amsthm,fixfoot}

@@

\title{PhD Thesis}
\author{Paolo G. Giarrusso}
\begin{document}
\maketitle
\section*{Abstract}
% Programs manipulating data collections require

% \begin{abstract}
% \end{abstract}

@@

\chapter{Reifying collection queries}
\label{sec:ch-aosd13}

\input{aosd13/graphs/evalResLos}
\input{aosd13/paperBody}
\input{aosd13/aosd13-extended-appendixes}

\newcommand{\co}[1]{\code{#1}} %Adaptation between different interfaces

\input{newlhs/new}

\chapter{Incrementalizing simply-typed \TitleLambda{}-calculus}
\input{pldi14/agda}

\input{pldi14/sec-intro}
\input{pldi14/sec-change-theory}
\input{pldi14/sec-differentiate}
\input{pldi14/sec-practice}
\input{pldi14/sec-rw}
\input{pldi14/sec-concl}

% Appendixes
\input{pldi14/sec-evaluation}
\input{pldi14/sec-addendum}

\input{pldi14/sec-formal}

\input{pldi14/sec-change-structures}

@@

\pg{Plan for things that complete the original paper's story: add them by
  revising that text and in that chapter.}

\bibliography{Bibs/DB,Bibs/ProgLang,Bibs/SoftEng,Bibs/own}
\chapter*{Acknowledgments}
% From AOSD13
I thank Sebastian Erdweg for helpful discussions on
this project, Katharina Haselhorst for help
implementing the code generator, and the anonymous reviewers, Jacques Carette and Karl Klose
for their helpful comments on this chapter.
This work is supported in part by the European Research Council, grant \#203099 ``ScalPL''.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\documentclass{book}
\usepackage{mylhs2tex}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{comment}
\bibliographystyle{abbrvnat}
\input{packages}
\input{macros}

@@

\title{Optimizing and Incrementalizing Collection Queries by AST Transformations}
\author{Paolo G. Giarrusso}
\begin{document}
\maketitle
\input{pldi14/agda}

\section*{Abstract}
% Programs manipulating data collections require

% \begin{abstract}
% \end{abstract}
\tableofcontents

@@

\part{Optimizing collection queries by reification}
\label{sec:ch-aosd13}

\input{aosd13/graphs/evalResLos}
\input{aosd13/paperBody}

\part{Incrementalization}
\label{part:incr}
\input{pldi14/sec-preliminaries}
\input{pldi14/sec-intro}

% Include either-or, one includes the other.
%\input{change-theory-reconstruct}
\input{pldi14/sec-change-theory}
\input{pldi14/sec-change-equiv}

\input{pldi14/sec-differentiate}
\input{pldi14/sec-practice}
\input{pldi14/sec-concl}

% Appendixes, to integrate.
% \input{pldi14/sec-evaluation}
% \input{pldi14/sec-addendum}

@@

\input{new-stuff}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
